%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%   PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{tabularx}

\name{Grazyna Huzik} % Your name
\occupation{ Web Designer / Front-End Developer }
 % Your position
\address{Newtown, PA} % Your address
\address{+1-216-246-8249 \\ grazhina.guzik@gmail.com} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%   EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Belarusian State University of Informatics and Radioelectronics, Minsk} \hfill {\em July 2016} \\ 
The Institute of Information Technologies \\
B.S. in Web Design and Computer Graphics \smallskip

{\bf Belarusian State University, Minsk} \hfill {\em June 2016} \\ 
The Institute of Journalism \\
B.A. in Web Journalism % \\

\end{rSection}


%----------------------------------------------------------------------------------------
%   TECHNOLOGY SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Have experience with}

\begin{tabular}{ @{} >{\bfseries}p{6cm} @{\hspace{6ex}} l }

Graphics Software & Adobe Creative Suite(Photoshop, Illustrator, InDesign,\\ 
                  & Lightroom, After Effects), 3D Studio MAX, CorelDRAW, \\ 
                  & Corel PHOTO-PAINT \smallskip \\
Data Visualization Software & Tableau \smallskip\\
Mockup Tools      & Moqups, InVision \smallskip \\
Front-End Technologies   & HTML5, CSS3, SASS/SCSS, Less, Bootstrap \smallskip \\
Programming Languages  & JavaScript, PHP \smallskip \\
Content Management Systems & Wordpress, Joomla \smallskip \\ 
Server technologies    & Apache Web Server \smallskip \\
SQL Databases          & MySQL \smallskip \\
Operating Systems      & MacOS, Windows, Linux (Ubuntu) \smallskip \\

\end{tabular}

\end{rSection}


%----------------------------------------------------------------------------------------
%   LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Languages}

\begin{tabularx}{\textwidth}{@{} >{\bfseries}p{6cm} @{\hspace{6ex}} l }

Russian & Native Speaker \smallskip \\

Belarusian & Native Speaker \smallskip \\ 

English & Advanced \smallskip \\

\end{tabularx}

\end{rSection}


%----------------------------------------------------------------------------------------
%   WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work positions}

\begin{rSubsection}{Rubyroid Labs, LLC}{August 2016 - October 2016}{UX / UI Designer}{Minsk, Belarus}
\item Developed possible user scenarios.
\item Created wireframes and interactive prototypes.
\item Designed user interfaces.
\item Worked closely with a front-end developer.
\end{rSubsection}

\begin{rSubsection}{SocialJet}{August 2015 - November 2015}{Junior Graphic Designer}{Minsk, Belarus}
\item Created "selling" teasers and banners for social media.
\item Edited and retouched photos.
\item Made collages.
\item Worked on photomontage and photo manipulation.
\end{rSubsection}


\begin{rSubsection}{Streamline}{January 2014 - June 2014}{Technical Editor}{Minsk, Belarus}
\item Scanned books and documents (sometimes unformatted and damaged).
\item Edited and retouched scanned pages.
\item Restored damaged book covers and other scanned imagery. 
\end{rSubsection}

\begin{rSubsection}{Belinfocenter / 21.by}{August 2012 - February 2013 (FT) / February 2013 - February 2016 (PT) }{Journalist, SMM Manager}{Minsk, Belarus / Remote}
\item Wrote news stories, reports and interviews.
\item Worked on SEO of the website. 
\item Developed web-content (including surveys, contests, etc.).
\item Participated in creating video content.
\item Promoted the website on social media (VK, Facebook, Twitter, OK.ru).

\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%   INTERNATIONAL PROGRAMS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Participation in international programs}
\begin{rSubsection}{FOJO Media Institute (Linnaeus University)}{September 2014}{Intern}{Kalmar, Sweden}
\item Studied journalism at FOJO Media Institute.
\item Learned from journalists, photographers and editors at a local newspaper "Barometern".
\end{rSubsection}

\begin{rSubsection}{Students Exchange Program "Work and Travel USA"}{June - August 2014}{Exchange Student}{Cleveland, OH}
\item Visited the USA for the first time.
\item Worked at the restaurant.
\item Learned a lot about American culture.
\end{rSubsection}

\begin{rSubsection}{Students Program "Belarus — Lithuania: Youth Dialogue and Development"}{November 2013}{Participant}{Vilnius, Lithuania}
\item Attended meetings with EHU's Vise-Rector for Academic Affairs, members of ISM Students' Union and ex-Minister of Education and Science in Lithuanian Parliament.
\item Participated in numerous discussions about differences between Belarusian and Lithuanian systems of higher education and the role of students government in it.
\end{rSubsection}

\end{rSection}



\end{document}
